\Large \bf \vrsdust{0.7cm} \hspace{0.1in} Redstone: a Deterministic Simulation Testing Framework for Distributed Systems

### 2024-06-08 paper/paper.tex
Updated paper

{\fontsize{12}{15}\selectfont 
The core of the simulated testing framework is its test injection.
By introducing randomness into whether or not a network packet is dropped or replayed,
for example, the system is able to cover a breadth of ``environmental conditions",
so to speak,
that are harder to anticipate when designing the distributed system.

@@

{\fontsize{12}{15}\selectfont 
\texttt{NOTE: we are in the process of writing up this section, and will submit this in an amended version of the writeup tomorrow morning.}
% This section needs: at least 1 graph/table, explanations of what we evaluated and how, what the evaluation tells us.

>>>>

{\fontsize{12}{15}\selectfont 
The core of the simulated testing framework is its fault injection.
By randomly (over the randomness of seed generation, rather than just randomly per-run)
deciding whether a network will drop a packet,
for example, the system is able to cover a breadth of ``environmental conditions",
so to speak,
that are harder to anticipate when designing the distributed system.

@@

{\fontsize{12}{15}\selectfont 
% \texttt{NOTE: we are in the process of writing up this section, and will submit this in an amended version of the writeup tomorrow morning.}
% This section needs: at least 1 graph/table, explanations of what we evaluated and how, what the evaluation tells us.
We tested the Redstone system on two benchmark tasks,
compute and socket.
The compute task performs a lot of computation and merely confirms that Redstone doesn't get in the way when it isn't called.
The data seem to back this conclusion.
The socket task repeatedly opens and closes sockets,
in effect testing nothing but the overhead of repeated syscalls.
As such, we see that the overhead on syscalls using Redstone is nearly ten times what it is otherwise.
However, in the socket task, only about 6 nanoseconds were spent in Redstone proper:
the rest is the ovehead of using \texttt{ptrace}, a debugging tool,
as our way of intercepting calls.
Essentially, we're trying to drive an eighteen-wheeler through the Formula 1.

\textbf{Average User Time}
\begin{tabular}{|l|r r| r|}
\hline
Workload & Linux (ns) &  Redstone (ns) & Ratio \\
\hline
Compute & 1,122,191,202 & 1,158,614,972 & 1.0325 \\
Socket  & 2,333 & 21,804 & 9.3459 \\
\hline
\end{tabular}

\begin{figure}[h]
\includegraphics[width=0.45\textwidth]{redstone_performance.png}
\caption{Ratio of time to perform benchmark tasks between Redstone and vanilla Linux}
\end{figure}
